---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# tp

**Experimental, demo package**

Small wrapper package, primarily to demonstrate creation of tornado plots.

## Installation

You can install the development version of tp from R-Universe via:

```{r, eval=FALSE}

install.packages('tp', repos = c('https://timtaylor.r-universe.dev', 'https://cloud.r-project.org'))
```


## How to use

tp provides two main functions: `tornado_samples()` and `tornado_plot()`.

The first of these, `tornado_samples()` takes:

- A user-supplied, vectorised, input function;
- A set of distributions you wish to draw from that have a one-to-one matching
  to the aforementioned function's parameters. These must be from the 
  [distributions3](https://alexpghayes.github.io/distributions3/) package.
- A number of samples to draw for each parameter.

The function is just a small wrapper around lapply that loops over a functions
parameters, sampling one whilst fixing the others. In effect it just wraps a 
simple univariate sensitivity analysis, ensuring the output is formatted in a
usable way for the later plot function. The output is a tibble with class
**tornado_samples** and an additional attributes that gives the baseline value
calculated when setting each argument to it's distributions mean value.


```{r}
library(tp)
set.seed(1)

# Function with desired arguments
# NOTE: MUST be vectorised by the user and return a scalar value
fun <- function(cost_per_day, days, discount) cost_per_day * days * discount

# A distribution (from distributions3) for each function argument
distributions <- list(
    cost_per_day = distributions3::Gamma(shape = 9, rate = 0.5),
    days         = distributions3::Gamma(shape = 5, rate = 1),
    discount     = distributions3::Beta(alpha = 2, beta = 40)
)

# Number of samples to take for each argument
samples <- 1000

# generate the samples for each parameter
(dat <- tornado_sample(samples, fun, distributions))
```

`tornado_plot()` takes, as input, the output from `tornado_sample()` as well
as a character string specifying the type of tornado plot to create (**jitter**
or **maxmin**). The first of these simply plots the sample results against the
corresponding distribution that varies. The second options plots the
corresponding maximum and minimum values as a split bar chart.

```{r}
tornado_plot(dat)
tornado_plot(dat, type = "maxmin")
```


